\documentclass{article}
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{geometry}
\usepackage{caption}
\usepackage{indentfirst}
\usepackage[colorlinks,urlcolor=blue]{hyperref}
\usepackage{minted}
\usemintedstyle{autumn}
\setminted{linenos,breaklines,tabsize=4,xleftmargin=1.5em}
\geometry{left=3.0cm,right=3.0cm,top=3.0cm,bottom=4.0cm}
\title{VE482 Lab 5}
\author{Liu Yihao 515370910207}
\date{}

\begin{document}
\maketitle

\section{Generalities on GDB}
\begin{enumerate}
\item How to enable built-in debugging in gcc?

Use \mintinline{shell}{-g} when compiling.

\item What is the meaning of GDB?

The GNU Project Debugger

\item Compile the C program from homework 4 with debugging enabled.

\begin{minted}{c}
gcc -g -o ex4 ex4.c
\end{minted}

\end{enumerate}

\section{Basic use of GDB}
\begin{enumerate}
\item Find the homepage of the GDB project.

\url{https://www.gnu.org/software/gdb/}

\item What languages are supported by GDB?

Ada, C, C++, Objective-C, Pascal (and many other languages)

\item What are the following GDB commands doing:
\begin{itemize}
\item backtrace

Print a backtrace of the entire stack: one line per frame for all frames in the stack.
\item where

Same as backtrace.
\item finish

Execute until selected stack frame returns.
\item delete

Delete some breakpoints or auto-display expressions.
Arguments are breakpoint numbers with spaces in between.
To delete all breakpoints, give no argument.
\item info breakpoints

Status of specified breakpoints (all user-settable breakpoints if no argument).
\end{itemize}

\item What is -tui option for GDB?

The TUI mode is enabled by this option. The GDB Text User Interface (TUI) is a terminal interface which uses the curses library to show the source file, the assembly output, the program registers and GDB commands in separate text windows.

\item What is the ``reverse step" in GDB and how to enable it. Provide the key steps and commands.

Reverse debugging is added in GDB 7.0, supported on limited targets (including i386/amd64 linux), so I should use GDB $\geqslant$ 7.0 on Linux to enable it. There are a few commands:
\begin{itemize}
\item reverse-continue (`rc')

Continue program being debugged but run it in reverse
reverse-finish -- Execute backward until just before the selected stack frame is called
\item reverse-next (`rn')

Step program backward, proceeding through subroutine calls.
\item reverse-nexti (`rni')

Step backward one instruction, but proceed through called subroutines.
\item reverse-step (`rs') 

Step program backward until it reaches the beginning of a previous source line
\item reverse-stepi

Step backward exactly one instruction

\item set exec-direction (forward/reverse)

Set direction of execution.
All subsequent execution commands (continue, step, until etc.) will run the program being debugged in the selected direction.
\end{itemize}

Breakpoints and watchpoints will work in reverse -- allowing you for instance to proceed directly to the previous point at which a variable was modified.

\end{enumerate}

\section{API}

\end{document}
